GEOCACHE SITE - PLEASE READ

Congratulations, you've found it! Intentionally or not!

What is this hidden container sitting here for?  What the heck is this thing doing here with all these things in it?

It is part of a worldwide game dedicated to GPS (Global Positioning System) users, called Geocaching. The game basically involves a GPS user hiding "treasure" (this container and its contents), and publishing the exact coordinates so other GPS users can come on a "treasure hunt" to find it. The only rules are: if you take something from the geocache, you must leave something in the geocache, and you must write about your visit in the logbook. Hopefully, the person that hid this container found a good spot that is on public property and is not easily found by uninterested parties. Sometimes, a good spot turns out to be a bad spot, though.

IF YOU FOUND THIS CONTAINER BY ACCIDENT:

Great!  You are welcome to join us!  We ask only that you:
\begin{itemize*}
	\item Please do not move or vandalize the container. The real treasure is just finding the container and sharing your thoughts with everyone else who finds it.
	\item If you wish, go ahead and take something. But please also leave something of your own for others to find, and write it in the logbook.
	\item If possible, let us know that you found it, by visiting the website listed below.
\end{itemize*}
Geocaching is open to everyone with a GPS and a sense of adventure.  There are similar sites all over the world. Currently, the organization has its home on the Internet. Visit our website if you want to learn more, or have any comments:

http://www.geocaching.com

If this container happens to be sitting on private property and you wish it removed, please let us know. We apologize, and will be happy to move it.

